\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[letterpaper, total={6in, 9in}]{geometry}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{tikz}


\title{Algebra 4 - Miscellaneous}
\author{TSS Math Club}
\date{Feb 2023}

\begin{document}
\large

\maketitle

\section{Euqation}

\subsection{Definition}
Eequation is a statement that the values of two mathematical expressions are equal.
To solve a equation means to find the value of the unknow(s) so that the values of two mathematical expressions are equal.

\subsection{Tricks in solving equation}

\subsubsection{Factoring}
\vspace{40px}
\subsubsection{Quadratic Formula}
\vspace{40px}
\subsubsection{Subsitution}
\vspace{40px}
\subsubsection{Rational Roots Theorem}
\vspace{40px}
\subsubsection{Long divition}
\vspace{40px}
\pagebreak
\subsection{Problems}
\subsubsection{Solve}
$$x^4+x^2+1=0$$
\vspace{40px}

\subsubsection{Solve}
$$(x+1)(x+2)(x+3)(x+4)=3$$
\vspace{40px}

\subsubsection{Solve}
$$x^3 + 5 x^2 + 3 x - 4 = 0$$
\vspace{40px}

\section{Vieta's Theorem and Symetrical Polynomials}
\subsection{Vieta's Theorem}
In algebra, Vieta's formulas are a set of results that relate the coefficients of a polynomial to its roots. 

\pagebreak

\subsection{Symetrical Polynomials}
Definition:
\vspace{30px}
\subsection{Problems}
\subsubsection{Problem}
Solve $x, y$, given $x+y=2, xy=-3$.
\vspace{60px}
\subsubsection{2022 AMC 12B Q4}
For how many values of the constant $k$ will the polynomial $x^{2}+kx+36$ have two distinct integer roots?
\vspace{60px}
\subsubsection{2022 AMC 12A Q15}
The roots of the polynomial $10x^3-39x^2+29x-6$ are the height, length, and width of a rectangular box (right rectangular prism). A new rectangular box is formed by lengthening each edge of the original box by $2$ units. What is the volume of the new box?
\pagebreak
\section{Inequality and Estimation}

\subsection{Solve Inequality}

\subsubsection{Example: Solve the following inequality}
$$\frac{x^4-x^2}{(x^4-13x^2+36)^2} \ge 0$$
\vspace{60px}

\subsection{Use Inequality to Estimate}
\subsubsection{Example}
$a,b,c$ are postive real numbers, prove
$$\frac{a}{b+c}+\frac{b}{c+a}+\frac{c}{a+b} > \frac{1}{3}$$
\vspace{60px}

\subsubsection{Problem: 2010 AIME I Q5}
Positive integers $a$, $b$, $c$, and $d$ satisfy $a > b > c > d$, $a + b + c + d = 2010$, and $a^2 - b^2 + c^2 - d^2 = 2010$. Find the number of possible values of $a$.
\vspace{60px}

\pagebreak

\subsubsection{Problem: 2022 CSMC Part B Q2}

\begin{itemize}
    \item  Determine all real numbers $a > 0$ for which $\sqrt{a^2+a}=\frac{2}{3}$
    \item  For each positive integer $m$, determine the difference between $(m+\frac{1}{2})^2+(m+\frac{1}{2})$ and the nearest perfect square.
    \item  For every positive integer $n$, prove that the number of positive integers $c$ with $n<\sqrt{c+\sqrt{c}}<n+1$ is even.
\end{itemize}

\pagebreak
\subsubsection{Problem}
$p, q$ are positive integers, prove at least one of the following is not a perfect square.
\begin{itemize}
    \item $p^2+q$
    \item $q^2+4p$
\end{itemize}


\end{document}
